DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-26 ase2017/paper.tex
fixed typo
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a toll (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis. However, the Control System Tuner is unable to consider FWL effects during the design process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.

>>>>

Notably, there are toolboxes in MATLAB with functions and scripts to facilitate the 
digital system design and implementation~\cite{matlab-toolbox}. Indeed, there is a MATLAB 
Toolbox named as DSVerifier Toolbox~\cite{issta2017}, which automatically detects 
specific errors related to digital system design ({\it e.g.}, stability, limit cycle and overflow) 
using symbolic model checking techniques based on Boolean Satisfiability (SAT) and 
Satisfiability Modulo Theories (SMT) solvers. Pessoa~\cite{mazo2010pessoa} is another 
toolbox applied to the synthesis of correct-by-design digital controllers. 
In particular, Pessoa is based on approximate bisimulation, which allows control engineers to replace differential equations, 
describing a physical plant, by a respective finite-state machine. However, Pessoa does not take advantage of
recent advances in bit-accurate verification of programs to synthesize controllers w.r.t. FWL effects. MATLAB already offers a tool (Control System Tuner~\cite{autotuner}) for automatically designing controllers based on optimization solvers or graphical analysis. However, the Control System Tuner is unable to consider FWL effects during the design process.
As a result, there is no other MATLAB toolbox to perform digital controller synthesis based on 
program synthesis engines and considering the complete range of approximations, including time discretization, 
quantization effects, and finite-precision arithmetic and its rounding errors.
